---
title: "A Parser for nmrML"
bibliography: nmRIO.bib
output: word_document
---

Steffen Neumann (sneumann@ipb-halle.de), 
  Luis Filipe de Figueiredo (Luis.deFigueiredo@ebi.ac.uk)
  Jie Hao (j.hao@imperial.ac.uk)

## Introduction

The nmRIO package aims at providing a common interface to
several NMR data formats.

Cool R packages for NMR processing are e.g. rNMR [@Lewis09rNMRopensource]
and Batman [@Hao12BATMANRpackage].

## Example

A short example sequence to read data from a nmrML raw data file. 
First open the file:

```{r open the file}
library(nmRIO)

nmrMLfile <- system.file("examples/HMDB00005.nmrML", package = "nmRIO")

fid <- readNMRMLFID(nmrMLfile)

```` 
 
```{r plotFID, fig = TRUE, width = 5, height = 4 }
plot(Re(fid), type="l")
````
 
Luis: I also need to access the following parameters:
spectral width (ideally in ppm but can work out the one in Hz)
transmitter frequency. Later, for bruker files I also need the following data
group delay, dsp firmware version

```{r Mockup-nmrML-parameters}
  tree <- xmlTreeParse(nmrMLfile)
  root <- xmlRoot(tree)
  ## Get required parameters from nmrML
  irradiationFrequency <- as.double(xmlAttrs(xmlElementsByTagName(root, "irradiationFrequency", recursive = TRUE)[[1]])["value"])

  sweepWidth <- as.double(xmlAttrs(xmlElementsByTagName(root, "sweepWidth", recursive = TRUE)[[1]])["value"])

  numberOfDataPoints <- as.integer(xmlAttrs(xmlElementsByTagName(root, "DirectDimensionParameterSet", recursive = TRUE)[[1]])["numberOfDataPoints"])

  irradiationFrequency
  sweepWidth
  numberOfDataPoints

  spectrum <- Re(fft(fid, inverse=TRUE))
````

The rudimentary processing results in:

```{r plotSpectrum, fig = TRUE, width = 5, height = 4 }
plot(spectrum, type="l")
````


```{r writeNmrML}
## Mockup to write the spectrum back into the nmrML 
## as "processed data"

#b64string <- nmRIO:::binaryArrayEncode(spectrum, byteFormat="complex64", compression="gzip")
  
````


## Future plans

A lot.

## Session information

```{r label=sessioninfo,echo=FALSE,cache=FALSE}
  sessionInfo()
```` 

